The \dealii{} Library, Version 9.2

### 2020-06-15 9.2/paper.tex
Add another name to the Acknowledgments section

\hypersetup{
  pdfauthor={
     Daniel Arndt,
     Wolfgang Bangerth,
     Bruno Blais,
     Thomas C. Clevenger,
    Marc Fehling,
    Alexander V. Grayver,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Jean-Paul Pelteret,
    Reza Rastak,
    Ignacio Thomas,
    Bruno Turcksin,
    Zhuoran Wang,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}

>>>>

\hypersetup{
  pdfauthor={
     Daniel Arndt,
     Wolfgang Bangerth,
     Bruno Blais,
     Thomas C. Clevenger,
%     Denis Davydov,
    Marc Fehling,
%     Daniel Garcia-Sanchez,
    Alexander V. Grayver,
%     Graham Harper,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Peter Munch,
%     Ross Maguire Kynch,
    Matthias Maier,
    Jean-Paul Pelteret,
    Reza Rastak,
    Bruno Turcksin,
    Zhuoran Wang,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.2, 2020},
}
